\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-03 evaluation.tex
confirm group 2's vanish bug

We also note that though group 2 stopped using Landslide after getting it to explore the minimal decision tree, if they had configured decision points around \texttt{mutex\_lock} (which was the recommended next step in the process), they would have found a subtle race in the reparenting section of their \texttt{vanish} code using the \texttt{vanish\_vanish} test.\footnote{
We have not confirmed this with Landslide. We will before submitting this thesis. % TODO
}
This bug is similar to the LudicrOS vanish/vanish bug studied in Section~\ref{sec:eval-casestudy}, and would have required a complicated redesign of the \texttt{vanish} implementation.

>>>>

We also note that though group 2 stopped using Landslide after getting it to explore the minimal decision tree, if they had configured decision points around \texttt{mutex\_lock} (which was the recommended next step in the process), they would have found a subtle race in the reparenting section of their \texttt{vanish} code using the \texttt{vanish\_vanish} test. We verified this by having an ex-TA re-instrument their kernel and add the decision points: from the time of exploring a minimal decision tree to finding the bug with the new decision set took half an hour of work, and fully understanding the nature of the bug took an hour on top of that.

This bug is similar to the LudicrOS vanish/vanish bug studied in Section~\ref{sec:eval-casestudy}, and would have required a complicated redesign of the \texttt{vanish} implementation to fix.
